\documentclass{article}

\usepackage{fullpage}
\usepackage{hyperref}
\hypersetup{
  colorlinks = true
}
\usepackage{listings}
\lstset{basicstyle=\ttfamily\footnotesize,breaklines=true}


\title{Homework 1---ECE590--001}
\date{1/15/2020}
\begin{document}
\maketitle
\begin{enumerate}
\item
  Install Docker on your local machine. Docker is available for Windows, Mac,
and Linux. You have succeeded when the following works.
\item
  Run your first Docker commands:
  \begin{enumerate}
  \item 
    \begin{lstlisting}[language=bash]
      docker pull continuumio/anaconda3 # pull the docker image from the container registry
      docker run -i -t continuumio/anaconda3 /bin/bash # run the image interactively
      # you will not have a root prompt within an anaconda3 containers
      exit # exits the terminal session (/bin/bash) and closes terminates the container
    \end{lstlisting}
  \item Read more \url{https://hub.docker.com/r/continuumio/anaconda3}. {\em try the last command
      to get an interactive jupyter notebook bridged from docker to your local machine}
  \end{enumerate}
\item
  Install \href{https://github.com/openai/spinningup}{spinningup} and its
dependencies by docker container and issuing commands. It is installed
correctly when you can run the algorithms provided.
\begin{enumerate}
\item Start by experimenting:
  \begin{lstlisting}[language=bash]
    docker run -i -t continuumio/anaconda3 /bin/bash
    git clone https://github.com/openai/spinningup # !!! these changes are not persistent
    pip install spinningup # use pip on local copy to install spinning up
  \end{lstlisting}
\item The dependencies will not be met by the {\tt pip} command above. But you can pip these
  requirements into the base anaconda environment. The requirements can be found:
  \url{https://github.com/openai/spinningup/blob/master/setup.py} and the command would be something
  like
  \begin{lstlisting}[language=bash]
    pip install ``req1'' ... ``reqN''
  \end{lstlisting}
\item The last pip command will not succeed (i.e. run to completion without errors). Read these errors and try to fix them.
  {\em The errors are due the fact that you have minimal development environment within the Docker container, you need to install more software and libraries,
    in particular, you likely need c/c++ compilers to support certain requirements that were within setup.py}. Figure out
  what these are and write them down. Additionally, how did you install them? {\em Hint: {\tt apt install} is the package management system in Debian and can install
    most things.}
  \begin{lstlisting}[language=bash]
    apt install emacs # installs emacs text editor
    apt install g++ gcc # installs gnu c++ and c compilers
  \end{lstlisting}
\item Run something from Spinning Up:
  \begin{lstlisting}[language=bash]
    python spinup/examples/bench_ppo_cartpole.py
  \end{lstlisting}
\end{enumerate}
\item
  From github (you will need to establish a github account), Fork {\tt
spring2019ECE590hineman} to a copy of the repository in your own name space.
Clone a copy of the repo from your name space (you can version control your work
this way).
\item
  So far we have executed docker from an image and editted it, we would now like
to build an image locally from a dockerfile that includes all the dependencies
we have for spinning up in persistent and repeatable way. There is already a
directory in {\tt spring2019ECE590hineman/homework/1/solutions} that contains a
skeleton dockerfile. Edit this file to install spinning up and its dependencies.
Show that you've succeed by screening shotting
\begin{lstlisting}[language=bash]
  python spinup/examples/bench_ppo_cartpole.py
\end{lstlisting}
You'll use what you learned from the last exercise to complete this.
\end{enumerate}
\end{document}
